Parsing Postfix log files

### 2008-04-10 doc/logparser.tex
Tested AWStats with my 93 log files, and wrote about it in the AWStats review.

\newcommand{\numberOFrules}[0]{%
    161%
}

@@

XXX TEST OTHER PARSERS ON THE 93 TEST LOG FILES\@.

@@

XXX DOWNLOAD\@: PFLOGSUMM, SAWMILL AND ANTEATER\@.

CHECK PARSING FOR THE FOLLOWING\@:

@@

    \item Pflogsumm
    \item Sawmill Universal Log File Analysis and Reporting
    \item Splunk
    \item Isoqlog
    \item AWStats
    \item Log analyser --- throughput monitor
    \item Anteater
    \item Yet Another Advanced Logfile Analyser
    \item Logparser/Lire
    \item Logrep
    \item Log Mail Analyser

@@

Parsing efficiency is an obvious concern when the parser routinely needs to
deal with 75 MB log files containing 300,000 log lines (generated daily on
a mail server handling mail for approximately 700 users --- large scale
mail servers would have much larger log files on a daily basis).  When
generating the data for the graphs included in \sectionref{graphs},
\numberOFlogFILES{} log files (totaling 10.08 GB, 60.72 million log lines)
were each parsed 10 times, the first run discarded, and the execution time
for the remaining 9 runs averaged.  The first run is discarded for two
reasons:

@@

>>>>

\newcommand{\numberOFrules}[0]{%
    165%
}

\newcommand{\numberOFlogLINES}[0]{%
    60,721,709%
}

\newcommand{\numberOFlogLINEShuman}[0]{%
    60.72 million%
}

@@

@@

XXX TEST OTHER PARSERS ON THE 93 TEST LOG FILES\@:

@@

    \item Pflogsumm
    \item Sawmill Universal Log File Analysis and Reporting
    \item Splunk
    \item Isoqlog
    \item Log analyser --- throughput monitor
    \item Anteater
    \item Yet Another Advanced Logfile Analyser
    \item Logparser/Lire
    \item Logrep
    \item Log Mail Analyser

@@

Parsing efficiency is an obvious concern when the parser routinely needs to
deal with 75 MB log files containing 300,000 log lines (generated daily on
a mail server handling mail for approximately 700 users --- large scale
mail servers would have much larger log files on a daily basis).  When
generating the data for the graphs included in \sectionref{graphs},
\numberOFlogFILES{} log files (totaling 10.08 GB, \numberOFlogLINEShuman{}
log lines) were each parsed 10 times, the first run discarded, and the
execution time for the remaining 9 runs averaged.  The first run is
discarded for two reasons:

@@

When tested with the \numberOFlogFILES{} test log files AWStats' report
says it parsed 9,240,075 (88.70\%) log lines out of 10,416,129, with
1,176,050 (11.29\%) corrupt lines; however there are actually
\numberOFlogLINES{} lines in the \numberOFlogFILES{} log files.  AWStats
actually parsed 17.15\% of the input lines, ignoring the remaining 82.85\%.
The graphs it produces give an overview of mails received for the last
calendar month, showing:

    \item The number of mails accepted from each host.

    \item How many mails were received by each recipient.

    \item The average number of mails accepted by the server per day and
        per hour.

    \item A top ten list of aggregated \SMTP{} error codes, e.g.\ the first
        entry in the list is: \texttt{Requested mail action not taken:
        relaying not allowed, unknown recipient user, \ldots}

% Parsed lines in file: 10416129
%  Found 4 dropped records,
%  Found 1176050 corrupted records,
%  Found 0 old records,
%  Found 9240075 new qualified records.
